# Results

## Residents Vaccinated

In this part, we want to explore whether there is a relationship between vaccinated people's residency, age and race. The data we use is loaded from `by-residency-demo.csv`.

The following mosaic chart show the residency and age of NYC residents who are vaccinated for COVID-19. We can the proportion of children who were vaccinated was higher among New Yorkers than among non-New Yorkers and the proportion of adult who were vaccinated was lower among New Yorkers than among non-New Yorkers.

```{r echo=FALSE}
library(vcd)
library(grid)

residency_vacc <- read.csv("./data/by-residency-demo.csv", sep = ',', header = T)
residency_vacc[residency_vacc=='Unknown'] <- NA #Unknown
residency_vacc[residency_vacc=='UNKNOWN'] <- NA #UNKNOWN
residency_vacc[residency_vacc=='Other'] <- NA #Other
residency_vacc[residency_vacc=='All ages'] <- NA #Other
residency_vacc[residency_vacc=='Native American/Alaska Native'] <- NA
residency_vacc[residency_vacc=='Native Hawaiian/Pacific Islander'] <- NA	
residency_vacc[residency_vacc=='Multiracial'] <- NA
residency_vacc=na.omit(residency_vacc)
df <- data.frame(residency_vacc[,-1])
df[4]=as.numeric(unlist(df[4]))

table1<-xtabs(COUNT_1PLUS_CUMULATIVE ~RESIDENCY+AGE_GROUP, df)
p1 <- mosaic( ~RESIDENCY+AGE_GROUP, table1, shade=TRUE, legend=TRUE, color=TRUE, gp_varnames = gpar(fontsize = 12, fontface = 1), gp_labels = gpar(fontsize = 7))
```

The following mosaic chart show the residency and age of NYC residents who are vaccinated for COVID-19. We can conclude that among black populations, middle-aged adults are less likely to be vaccinated than children and the elderly; whereas in the Asian and Latinos group, compared with children and the elderly, the willingness to vaccinate is stronger among the middle-aged。

```{r echo=FALSE}
table2<-xtabs(COUNT_1PLUS_CUMULATIVE ~AGE_GROUP+RACE_ETHNICITY, df)
p2 <- mosaic( ~AGE_GROUP+RACE_ETHNICITY, table2, shade=TRUE, legend=TRUE, color=TRUE, gp_varnames = gpar(fontsize = 12, fontface = 1), gp_labels = gpar(fontsize = 7))
```

The following mosaic chart show the residency and age of NYC residents who are vaccinated for COVID-19. We can see that Asians, blacks and Latinos living in New York are more open to vaccinations than those who are non-residents

```{r echo=FALSE}
table3<-xtabs(COUNT_1PLUS_CUMULATIVE ~RESIDENCY+RACE_ETHNICITY, df)
p3 <- mosaic( ~RESIDENCY+RACE_ETHNICITY, table3, shade=TRUE, legend=TRUE, color=TRUE, gp_varnames = gpar(fontsize = 12, fontface = 1), gp_labels = gpar(fontsize = 7))
```
